Modal Abstractions for Virtualizing Memory Addresses

### 2023-02-27 programlogic.tex
+

One might have already observed that this virtual points-to definition is too strong to specify any virtual memory operations, some of which we explain within as part of experiement in Section \ref{}, require reasoning of sharing of physicall pages accross virtual memory addresses because this strong virtual points-to relation doesn’t care about owning those fractional resources, it only cares that something ensures the correct page table walk exists. Therefore we need to weaken the virtual-pointsto to capture the acutal sharing accross the virtual addresses.

One possible approach to resolving this is to identify and separate the type of ownership within and outside the virtual points-to relation. Iris has a ghost map resource where fragmental-ownership of an individual key-value pair (per-element) can be handled as a resource. We use this mechanism to separate the virtual-to-physical translation from the physical memory involved: virtual points-to assertions can be defined in terms of fragmental ownership (ownership of an element) of these partial ghost map entry assertions, plus sharing an invariant that the current installed page table respects all entries of the mapping as shown in Figure \ref{}. Unmapping collects the authoritative map kvpairs from collecting the assertions, and then can remove them from the ghost map and update the page tables. Critically, physical full ownership of the page tables then lives in the invariant on the current page table, so some virtual pointsto as- sertions can refer to memory in those page tables. This still works with the modality, since that invariant is also semantically a predicate on a page table root.

>>>>

One might have already observed that this virtual points-to definition is too strong to specify virtual memory operations, some of which we explain within as part of experiement in Section \ref{}, which  requires reasoning of sharing physical pages across different virtual memory addresses. Although there seems to fractional permissions for fragmental ownership of page-table entries, strong virtual points-to (in Figure \ref{strongvirtualpointsto}) relation doesn’t care about owning those fractional resources, it only cares that something ensures the correct page table walk exists. Therefore we need to weaken the virtual-pointsto to capture the acutal sharing accross the virtual addresses.

One possible approach to is to just abstracting the \textit{valid} page-table walk existence from a each virtual address (e.g. \textsf{va}) to a physical page address, as \textit{per-element} ownership of a logical \textit{page-table-walk-summarization-map}
\[\mathcal{M}\textsf{PTableWalk} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \;  (\mathcal{W}_{64} \; \rightarrow_{\textrm{fin}}\;  (\textsc{Frac }, \mathord{+}) \times (\textsc{Agree } \Loc,\mathord{=}) ))\]
provided by a fragmentery ghost resrource ownership of $\mathcal{M}\textsf{PTableWalk}$. \todo[inline,color=red]{stop here}tranresolving this is to identify and separate the type of ownership within and outside the virtual points-to relation. Iris has a ghost map resource where fragmental-ownership of an individual key-value pair (per-element) can be handled as a resource. We use this mechanism to separate the virtual-to-physical translation from the physical memory involved: virtual points-to assertions can be defined in terms of fragmental ownership (ownership of an element) of these partial ghost map entry assertions, plus sharing an invariant that the current installed page table respects all entries of the mapping as shown in Figure \ref{}. Unmapping collects the authoritative map kvpairs from collecting the assertions, and then can remove them from the ghost map and update the page tables. Critically, physical full ownership of the page tables then lives in the invariant on the current page table, so some virtual pointsto as- sertions can refer to memory in those page tables. This still works with the modality, since that invariant is also semantically a predicate on a page table root.
